%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10.5pt]{letter} % Default font size of the document, change to 10pt to fit more text

%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
\usepackage{helvet} % Uncomment this (while commenting out the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------
\begin{letter}{Dr. Traci Arden \\
Department of Anthropology Chair \\
University of Miami \\
PO Box 248106 \\
Coral Gables, FL 33124-2005}

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{flushright}
\large\bf Gentry Hanks \\ % Your name
\vspace{15pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
gENTRYhANKS@gmail.com \\
19525 SW 128th Ave \\ 
Miami, FL 33177 \\ 
(305) 504-1623 \\% Your address and phone number
\end{flushright} 
%\vfill

\signature{Gentry Hanks} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dr. Traci Ardren,} 

%PARAGRAPH ONE: 
I hope this letter finds you well. Please consider this as part of my application for the position of lecturer in Anthropology advertised on the University of Miami website. I'll try to leave out the most atrocious cover letter cliches to keep this short as you must have many applications. My MA in human geography is from the Department of Geography \& Anthropology at LSU. I am currently a PhD candidate in the department of Geography at Queen's University in Kingston, Ontario Canada. I recently moved to Miami, where I am writing my dissertation on medical, historical, cultural and emotional landscapes of diabetes.
%PARAGRAPH TWO: 

The University of Miami has a wonderful teaching and research reputation. The same commitment to critical pedagogy that inspires my teaching also propels my research and my insatiable quest for knowledge, its creation and how it becomes legitimate certainly inspires my teaching. My diverse teaching experiences and the pertinence of medical anthropology to my own work in cultural and health geographies makes me a dynamite candidate for this position! 
I have taught undergraduates since 2011 as a teaching assistant and guest lecturer (see CV for details). Prior to teaching at Queen's University, I taught Latin and Spanish in secondary education for 4 years and ESL abroad for 2 years. 
In my dissertation research I use qualitative methods such as body mapping and text mining of public online forum discourse. qualitative research on personal biomedical waste for The Canada Waste Flow Project has lead to a collaboration on a book for Ashgate titled \textit{Throw Away Societies: People, Place \& Waste}. My contribution, chapter 1, \textit{Diabetic Debris: Social Media Discourses on Personal Biomedical Waste Flows in North America} uses social media data to examine the gap between practices of disposing personal biomedical waste in everyday life and waste policy in North America. 
 
%PARAGRAPH THREE: 
If I have piqued your interest and you feel I am a qualified and appropriate candidate for this position, I would be quite keen to meet with you. Contact information for my references is included in my CV, but please do let me know if you would like me to request that a letter from each be sent under separate cover. Upon your request, I am more than willing to send additional materials. I look forward to hearing from you.
% Request a personal interview and indicate your flexibility as to the time and place. Repeat your phone number in the letter and offer assistance to help in a speedy response. For example, state that you will be in the city where the company is located on a certain date and would like to set up an interview. Alternatively, state that you will call on a certain date to set up an interview. End the letter by thanking the employer for taking time to consider your credentials. 

\closing{Sincerely yours,}


\encl{Curriculum Vitae} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}